Analysis-ready VCF at Biobank-scale using Zarr

### 2024-05-08 diagrams/data-model.tex
Tweaks

%% compresion
 \node (numcodecs) [rectangle, draw, densely dotted, thick, rounded corners, minimum width=2.4cm, minimum height=2.6cm, anchor= south west]
    at (4.8,2.2) {};
 \node[anchor=north,below] at (numcodecs.north) {\scriptsize Filter \& compress};
 %\node[anchor=south,below] at (numcodecs.south) {numcodecs};
 \node (blosk) [rectangle, ultra thick, red, draw, rounded corners, minimum width=1.8cm, minimum height=1.6cm, anchor=center,align=center,text=black]
    at (numcodecs) {\scriptsize Blosc\\\scriptsize ZSTD\\\scriptsize BITSHUFFLE};
 \draw[ultra thick, red,-stealth] (3.9,3.5,-.25) -- (5,3.5,-.25);

>>>>

%% compresion
 \node (numcodecs) [rectangle, draw, densely dotted, thick, rounded corners, minimum width=2.4cm, minimum height=2.6cm, anchor= south west]
    at (4.8,2.2) {};
 \node[anchor=north,below] at (numcodecs.north) {\scriptsize Filter \& compress};
 %\node[anchor=south,below] at (numcodecs.south) {numcodecs};
 \node (blosk) [rectangle, ultra thick, red, draw, rounded corners, minimum width=1.8cm, minimum height=1.6cm, anchor=center,align=center,text=black]
    at (numcodecs) {\scriptsize Blosc\\\scriptsize Zstandard\\\scriptsize BITSHUFFLE};
 \draw[ultra thick, red,-stealth] (3.9,3.5,-.25) -- (5,3.5,-.25);

### 2024-05-08 paper.tex
Tweaks

Fig~\ref{fig-data-storage} shows compression performance 
on up to a million samples for chromosome 21.
Unsurprisingly, gzipped compressed VCF requires the most 
storage, with BCF providing substantially better compression
performance (note the log-log scale). Genozip has 
superb compression, having far smaller file sizes that the 
other methods (although somewhat losing its advantages at 
larger sample sizes). Zarr and Savvy have 
almost identical compression performance in this example.
It is remarkable that the simple approach of compressing
two dimensional chunks of the genotype matrix 
using the Zstandard compressor~\citep{collet2021rfc} and the 
bit-shuffle filter from Blosc~\cite{alted2010modern} produces 
compression levels competitive with the highly specialised methods
used by Savvy.

>>>>

Fig~\ref{fig-data-storage} shows compression performance 
on up to a million samples for chromosome 21.
Unsurprisingly, gzip compressed VCF requires the most 
storage, with BCF providing substantially better compression
performance (note the log-log scale). Genozip has 
superb compression, having far smaller file sizes that the 
other methods (although somewhat losing its advantages at 
larger sample sizes). Zarr and Savvy have 
almost identical compression performance in this example.
It is remarkable that the simple approach of compressing
two dimensional chunks of the genotype matrix 
using the Zstandard compressor~\citep{collet2021rfc} and the 
bit-shuffle filter from Blosc~\cite{alted2010modern} produces 
compression levels competitive with the highly specialised methods
used by Savvy.
